### 2021-04-04 Chapter-3/Chapter-3.tex
update

                         &                        &                     &                      &                 & minutes            \\\cline{7-7}
      RSA &    mbedTLS 2.5   & 6            & 6          & 0                    & 22,109,246    & 39      \\
      RSA &    mbedTLS 2.15    & 12          & 12     & 0                    & 24,484,441    & 44        \\
      RSA &     OpenSSL 0.9.7      & 107     & 105           & 2                    & 17,002,523   & 23  \\
      RSA &    OpenSSL 1.0.2f      & 38                     & 27                  & 11                   & 14,468,307   & 29    \\
      RSA &   OpenSSL 1.0.2k      & 36              & 27                  & 9                    & 15,285,210   & 40      \\
      RSA &          & 31                     & 22                  & 9                    & 16,390,750   & 34      \\
      RSA &         & 4                      &  4                  & 0                    & 18,207,016   & 8         \\
      RSA &            & 8                      &  8                  & 0                    & 18,536,796    & 5       \\
      RSA & & 11& 9& 2& 9,527,231& 2 \\
      RSA & & 14& 14& 0& 10,513,606& 14  \\
      RSA &        & 8                      &  8                  & 0                    & 27,407,986    & 113    \\

>>>>

                         &                        &                     &                      &                 & minutes            \\\cline{7-7}
      RSA &    mbedTLS 2.5   & 6            & 6          & 0                    & 22,109,246    & 39      \\
      RSA &    mbedTLS 2.15    & 12          & 12     & 0                    & 24,484,441    & 44        \\
      RSA &     OpenSSL 0.9.7      & 107     & 105           & 2                    & 17,002,523   & 23  \\
      RSA &    OpenSSL 1.0.2f      & 38                     & 27                  & 11                   & 14,468,307   & 29    \\
      RSA &   OpenSSL 1.0.2k      & 36              & 27                  & 9                    & 15,285,210   & 40      \\
      RSA &   OpenSSL 1.1.0f       & 31           & 22                  & 9                    & 16,390,750   & 34      \\
      RSA &  OpenSSL 1.1.1       & 4                      &  4                  & 0                    & 18,207,016   & 8         \\
      RSA &  OpenSSL 1.1.1g      & 8                      &  8                  & 0                    & 18,536,796    & 5       \\
      RSA & Libgcrypt 1.6.1 & 11& 9& 2& 9,527,231& 2 \\
      RSA & Libgcrypt 1.7.3 & 14& 14& 0& 10,513,606& 14  \\
      RSA & Libgcrypt 1.8.5 & 8                      &  8                  & 0                    & 27,407,986    & 113    \\
